Final Project Submission

### 2021-05-13 code/Submission.Rmd
slight tweaks

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)      
library(ggplot2)      
library(colorspace)   #better colors for ggplot
library(tidyverse)    
library(dplyr)
library(gridExtra)
library(viridis)
library(ggridges)
library(broom)
library(stargazer)
library(corrr)
library(GGally)
library(RColorBrewer)
library(grid)
library(likert) # for creating a likert plot
library(kableExtra) # not needed but makes the table nicer
echoval <- F
load("../../Pew/pewTech.RData")
```

@@

###Data Viz###
## Centerd, No Percents 
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(title = "Key Figure 2:",
    subtitle = title2,
    caption = "This graph shows a representative sample of the US population’s trust in the\nresponsible use of facial recognition across three different groups.\nIt is clear to see that people trust law enforcement even though law enforcement\nboth has a history of abusing facial recognition technology\n and that current facial recognition systems\n are highly flawed and struggle to accurately identify people of color.\n\nData sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

@@

```{r central_fig_alt, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others'\ninformation","Keep their\nown information\nprivate", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49, fill = as.factor(sumRTBF))) +
  geom_bar() +
  labs (
    title = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" by Stance on Personal Data",
    x = "Participants find it more important to...",
    y = "",
    caption = c("Alternate Key\nFigure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  scale_fill_brewer(palette="YlGnBu", name = "How many of the following categories\nof data should fall under the Right To Be Forgotten:\n   -Data collected by law enforcement\n   -Employment history or work record\n   -Negative media coverage\n   -Potentially embarassing photos or\n     videos", labels=c("None","One","Two","Three","Four"))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
```
This visualization does both things that we would like it to do: it makes immediately apparent the difference in scale between those who prioritize public data versus private, and it has a clear color-coded breakdown of how many categories of data each class thinks should be protected. However, it is clunky and makes it harder to closely examine the distribution of sum counts than it is in our final graphic. As Healy breaks down, bad design is plagued by bad perception; stacking the boxes for each number makes it hard to directly compare the distribution of counts by not having a common base. This in turn warps our perception of the final data. So while this tells a similar story to the one up above, we ended up making additional aesthetic decisions to better convey that information in a clear and pleasing way.

@@

```{r FACE3 Alt, echo=echoval, message=FALSE}
## 100% BarPlot
plot(likert(df_f3[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(caption = c("Alternate Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

@@

```{r, echo=F, message=FALSE}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)      
library(ggplot2)      
library(colorspace)   #better colors for ggplot
library(tidyverse)    
library(dplyr)
library(grid)
library(gridExtra)
library(broom)
library(GGally)
library(RColorBrewer)
library(likert) #for creating a likert plot
library(kableExtra) # not needed but makes the table nicer
echoval <- F
load("../../Pew/pewTech.RData")
```

@@

###Data Viz###
## Centerd, No Percents 
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(title = "Key Figure 2:",
    subtitle = title2,
    y = "\n\n This graph shows a representative sample of the US population’s trust in\nthe responsible use of facial recognition across three different groups. It is\nclear to see that people trust law enforcement even though law enforcement\nboth has a history of abusing facial recognition technology and that current\nfacial recognition systems are highly flawed and struggle to accurately\nidentify people of color.",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

@@

```{r central_fig_alt, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others'\ninformation","Keep their\nown information\nprivate", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49, fill = as.factor(sumRTBF))) +
  geom_bar() +
  labs (
    title = "Alternate Key Figure 1:",
    subtitle = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" by Stance on Personal Data",
    x = "Participants find it more important to...",
    y = "",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  scale_fill_brewer(palette="YlGnBu", name = "How many of the following categories\nof data should fall under the Right To Be Forgotten:\n   -Data collected by law enforcement\n   -Employment history or work record\n   -Negative media coverage\n   -Potentially embarassing photos or\n     videos", labels=c("None","One","Two","Three","Four"))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
```
This visualization does both things that we would like it to do: it makes immediately apparent the difference in scale between those who prioritize public data versus private, and it has a clear color-coded breakdown of how many categories of data each class thinks should be protected. However, it is clunky and makes it harder to closely examine the distribution of sum counts than it is in our final graphic. As Healy breaks down, bad design is plagued by bad perception; stacking the boxes for each number makes it hard to directly compare the distribution of counts by not having a common base. This in turn warps our perception of the final data. So while this tells a similar story to the one up above, we ended up making additional aesthetic decisions to better convey that information in a clear and pleasing way.

@@

```{r FACE3 Alt, echo=echoval, message=FALSE}
## 100% BarPlot
plot(likert(df_f3[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  labs(title = "Alternate Key Figure 1:",
       subtitle = title2,
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

@@
